Check Coverage

### 2019-10-22 analysis/merge_data.Rmd
Merge conflict

get_fd <- function(data, study, plot){
  print(max(data$record_id))
  species_mat <- data %>%
    select(year, id) %>% 
    distinct() %>%
    arrange(year, id) %>%
    mutate(present = 1) %>%
    spread(id, value = present, fill = 0) %>%
    select(-year)

@@

  as.tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .) %>%
    mutate(study_id = study, plot = plot, n_traits = ncol(trait_mat)) %>%
    write_tsv(paste0(here::here("data"), "/fd_output/", "s", study, "_p", plot, "_fd.tsv"))
}

@@

data <- biotime_traits %>% 
  filter(!is.na(plot)) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  filter(study_id == 516)

@@

fd <- map_df(combs, ~ get_fd_safe(data = data, study = .x[1], plot = .x[2]))  
```

Read data back in:
```{r}
# files <-  dir(here::here("data", "fd_output"), "*.tsv")
# 
# fd_data <- files %>%
#   paste0(here::here("data", "fd_output"), "/", .) %>%
#   map_dfr(read_tsv)
# 
# fd <- biotime_traits %>% 
#   filter(!is.na(plot), !study_id %in% c(195, 360)) %>%
#   anti_join(fd_data) %>%
#   group_by(study_id, year, plot) %>%
#   filter(n_distinct(id) > 4) %>%
#   ungroup() %>%
#   group_by(study_id, plot) %>%
#   group_map(~get_fd_safe(.x, study = .y$study_id, plot = .y$plot))
# 
# #4610981
# #7611121

>>>>

get_fd <- function(data, study, plot_num){
  print(max(data$record_id))

  data <- data %>%
    filter(study_id == study, plot == plot_num)

  species_mat <- data %>%
    select(year, id) %>% 
    distinct() %>%
    arrange(year, id) %>%
    mutate(present = 1) %>%
    spread(id, value = present, fill = 0) %>%
    select(-year)

@@

  as_tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .) %>%
    mutate(study_id = unlist(study), plot = unlist(plot_num)) %>%
    write_tsv(paste0(here::here("data"), "/fd_output/", "s", study, "_p", plot_num, "_fd.tsv"))
}

@@

data <- biotime_traits %>% 
  filter(!is.na(plot), !is.na(scientificName)) %>% #remove unlabeled plots and observations without traits
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  filter(study_id == 516)

@@

fd <- map_dfr(combs, ~ get_fd_safe(data = data, study = .x[1], plot = .x[2]))  
```

Read data back in:
```{r}
files <-  dir(here::here("data", "fd_output"), "*.tsv")

fd_data <- files %>%
  paste0(here::here("data", "fd_output"), "/", .) %>%
  map_dfr(read_tsv)

fd <- biotime_traits %>%
  filter(!is.na(plot), !study_id %in% c(195, 360)) %>%
  anti_join(fd_data) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  group_by(study_id, plot) %>%
  group_map(~get_fd_safe(.x, study = .y$study_id, plot = .y$plot))

#4610981
#7611121
